\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{authblk}
\usepackage{cite}
\usepackage{natbib}
\usepackage{dcolumn}
\usepackage{pdfpages}
\usepackage{epigraph} % Required for inspirational quote
% packages required for kable()
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\renewcommand{\epigraphsize}{\small}
\setlength{\epigraphwidth}{0.51\textwidth}
\renewcommand{\textflush}{flushright}
\renewcommand{\sourceflush}{flushright}

% display code
\usepackage{listings}
\usepackage{color}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\lstset{frame=tb,
  language=Java,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}


%\date{Draft -- please do not circulate.}

\title{SEM}

\author[1]{David Broska}

\begin{document}
\maketitle

In my previous study submitted for the multilevel modeling research report, I found that liberals/Democrats perceive online comments on average as more toxic than conservatives/Republicans. What explains this difference? Below, I will lay out meditation hypotheses to explore this question. 



\textbf{Data}

I will use the same data as for my multilevel modeling study. To study the determinants of perceived civility in conversations, we recruit 4,675 American adults via Prolific to fill out a survey asking them to evaluate Facebook conversations regarding perceived toxicity and other features. Respondents who did not pass an attention check were not allowed to take the survey. Excluding missing values\footnote{There is no evidence of differential attrition.}, the total sample size is 32,597 observations. Those who passed the attention check were randomly assigned to evaluate 7 conversations. Not every respondent evaluated each conversation; each one was evaluated 3.27 times on average. 

\end{document}